Hurricane Evacuation Strategies for the State of Mississippi

### 2015-11-16 manuscript.tex
Masterful data fudging

\title{Hurricane Evacuation Strategies for the State of Mississippi}
\author{Paul Chesnais (pmc85), Antoine Pourchet (app63), and Ryan Vogan (rcv39)\\2015 Cornell Mathematical Contest in Modeling\\November 16, 2015}
\date{}

@@

\section{Stochastic Model of Landfall-Avodiant Evacuations}
\label{sec:stochastic}
  \subsection{Model Description}

  \subsection{Parameter Values and Justification}
  \subsection{Results}
  \begin{figure}
    \center
    \begin{subfigure}[b]{0.5\textwidth}
      \center
      \includegraphics[width=\linewidth]{figures/pred_hancock-crop.pdf}
      \caption{Predicted Evacuation for Landfall in Hancock County}
    \end{subfigure}~
    \begin{subfigure}[b]{0.5\textwidth}
      \center
      \includegraphics[width=\linewidth]{figures/pred_jackson-crop.pdf}
      \caption{Predicted Evacuation for Landfall in Jackson County}
    \end{subfigure}
    \caption{}
  \end{figure}
  \subsection{Strengths and Weaknesses}

>>>>

\title{Hurricane Evacuation Strategies for the State of Mississippi}
\author{Paul Chesnais (pmc85), Antoine Pourchet (app63), and Ryan Vogan (rcv39)\\2015 Cornell Mathematical Contest in Modeling}
\date{November 16, 2015}

@@

\section{Stochastic Model of Landfall-Avodiant Evacuations}
\label{sec:stochastic}
  \subsection{Model Description}
    In this model, instead of giving citizens particular evacuation plan, we give them a simple rule.
  \subsection{Parameter Values and Justification}
  \subsection{Results}
  \begin{figure}
    \center
    \begin{subfigure}[b]{0.5\textwidth}
      \center
      \includegraphics[width=\linewidth]{figures/pred_hancock-crop.pdf}
      \caption{Predicted Evacuation for Landfall in Hancock County}
    \end{subfigure}~
    \begin{subfigure}[b]{0.5\textwidth}
      \center
      \includegraphics[width=\linewidth]{figures/pred_jackson-crop.pdf}
      \caption{Predicted Evacuation for Landfall in Jackson County}
    \end{subfigure}
    \caption{}
  \end{figure}
  \subsection{Strengths and Weaknesses}
